Toward theories of deliberated preferences

### 2020-11-12 simple.tex
No more parametric incompatibility relation

\subsection{Coherence and completeness}
%A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \prop') \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$. 
%Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$.
Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$. Let $\incompat \subseteq \Phi × \Phi$ denote the set of incompatible pairs of propositions.

@@

\subsection{Effectively comparing models}
\label{sec:compare}
Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory with an incompatibility relation $n$, say that they disagree about $(\prop, \propbar) \in n$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$. Say that they are incompatible iff there is at least one pair $(\prop, \propbar) \in \allprops$ that they disagree about.

@@

\begin{procedure}
	\label{proc}
	Pick any $\prop \in \allprops$ about which $\alpha$ and $\beta$ disagree.

>>>>

\subsection{Coherence and completeness}
\label{sec:coh}
Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $\forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'$. Let $\incompat \subseteq \Phi × \Phi$ denote the set of incompatible pairs of propositions.

@@

\subsection{Effectively comparing models}
\label{sec:compare}
Recall from \cref{sec:coh} that $\incompat = \set{(\prop, \prop') \suchthat \forall \hist \in \allhist: \hist \ileadsto \prop ⇒ \hist \nileadsto \prop'}$ denotes the set of pairs of incompatible propositions.
Given two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $(\prop, \propbar) \in \incompat$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$. Say that the theories are incompatible iff there is at least one pair $(\prop, \propbar) \in \incompat$ that they disagree about.

@@

\begin{procedure}
	\label{proc}
	Pick any $\prop, \propbar \in \incompat$ about which $\alpha$ and $\beta$ disagree.
